% This is a modification of an altacv.cls (v1.1.5, 1 December 2018) CV created by LianTze Lim (liantze@gmail.com)
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%%%%%%%%%%%%%%%%
%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper,ragged2e]{altacv}
%bib
\usepackage[backend=biber, style=authortitle]{biblatex}
\addbibresource{twentlingbib.bib}

%% AltaCV uses the fontawesome See texdoc.net/pkg/fontawecome

% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1cm,bottom=1cm}

\usepackage[sfdefault]{FiraSans} %% option 'sfdefault' activates Fira Sans as the default text font
\usepackage[T1]{fontenc}
\renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}

\usepackage{setspace}

% Change the colours if you want to
\definecolor{NiceCyan}{HTML}{00CC99}
\definecolor{NiceBlue}{HTML}{006080}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{NiceBlue}
\colorlet{accent}{NiceBlue}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\begin{document}
\name{Tristen Wentling}
\tagline{Applied Machine Learning Data Scientist}
%\photo{2.5cm}{tristen} %prefixed name of image file to use
\personalinfo{%
  \email{tristen.wentling@gmail.com}
  \phone{727-240-8089}
  \mailaddress{3874 Woodlake Cir Apt 166}
  \location{Palm Harbor, FL}
  \newline
  \linkedin{linkedin.com/in/tristenwentling}
   \github{github.com/tristenwentling} 
   \homepage{tristen.weebly.com/}
  }

%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% sidebar content filename
\cvsection[tristen-p1sidebar]{Experience}

\cvevent{Data Scientist}{The Depository Trust {\&} Clearing Corporation}{Apr 2018 --  present}{Tampa, FL}
\textit{Application Development Machine learning Specialist}
\begin{itemize}
\item  Designed and prototyped an ML deployment method allowing solutions to be deployed at scale and regulationally compliant in production.
\item Integrated an enterprise data science platform capable of supporting thousands of users on Jupyter, H2o Flow, and R Studio. 
\item Prototyped and developed ML solutions using clustering methods,  outlier detection, natural language processing, and classification methods for 3 different clients. 
\item Developed core ETL processes for a new revenue-generating data product and used it to deliver validation data for third party analysis and evaluation.
\end{itemize}

\divider

\cvevent{Data Scientist}{Nielsen Media Research}{Feb. 2017 -- Apr 2018}{Oldsmar, FL}
\textit{Local Television Custom Analytics and Client Inquiries}
\begin{itemize}
\item Engineered, integrated, and validated big data sources scaling local television reporting tools from hundreds to millions of data points.
\item Built custom machine learning regression models for client solutions as a part of multimillion dollar client support contracts.
\item Built video classification model for internal engineering leading to production implentation solution as well as a patent application.
\item Modernized a critical customer reporting tool (bash/SAS -> Spark/Python) used to generate reports for hundreds of client stations annually.
\item Developed new custom reporting tool for client reports on genre categorization alleviating concerns on the part of clients.
\end{itemize}

\divider

\cvevent{Graduate Teaching Assistant}{Kansas State University}{Jun 2016 -- Jan 2017}{Manhattan, KS}

\begin{itemize}
\item Recitation instructor for Calculus 1 and tutoring for College Algebra, Calculus 1, 2, and 3, Business Calculus, and Linear Algebra influencing over 100 students.
\end{itemize}

\divider

\cvevent{Graduate Teaching Assistant}{Missouri State University}{Aug 2014 -- May 2016}{Springfield, MO}

\begin{itemize}
\item Lecture instructor (5 sections) {\&} recitation instructor (2 sections) college algebra guiding over 200 students to success. Lead algebra test development for 2 semesters used for over 1000 algebra students.
\end{itemize}
\divider

\cvevent{Freelance Python Developer}{Upwork}{May 2014 -- Aug 2014}{Springfield, MO}

\begin{itemize}
\item Built data pipeline tooling and trained in deep learning methodology with Ersatz Labs during a critical additional funding round and public release.
\end{itemize}


%\clearpage


%% If the NEXT page doesn't start with a \cvsection but you'd
%% still like to add a sidebar, then use this command on THIS
%% page to add it. The optional argument lets you pull up the
%% sidebar a bit so that it looks aligned with the top of the
%% main column.
% \addnextpagesidebar[-1ex]{page3sidebar}


\end{document}
